\documentclass{article}

\usepackage{soul}

\title{Doggochain --- A doggo game blockchain}
\author{%
    Guilherme Christopher Michaelsen Cardoso (14100831) \\
    João Paulo Taylor Ienczak Zanette (14200743)
}

\begin{document}
    \maketitle

    \section{Idea}

    The Doggochain project is a game in which players may own and pet monsters,
    which will have their own \textit{stats} (values that characterize monsters
    with respect to their strength or vitality, for example), and interact with
    wild and other players' monsters, including collect, pet, feed, train and
    even trade.

    \section{Motivation}

    This idea was inspired by two games. One of them is CryptoKitties, an
    online game where you can buy and sell digital cats using ethereum, and
    breed them to create new cats. The game however is very simple and lacks
    much excitement other than the idea of obtaining rare combinations.

    The other game is Pokémon, a largely succesful game about capturing,
    training, breeding, and battling with pet-like monsters that aid the player
    in their adventures.

    By combining the two ideas, this project aims to create a blockchain-based
    RPG where the player is able to capture, train, and compete with their
    monsters, but also trade with other players, be it exchanges of monsters
    for other monsters, or for cryptocurrency.

    \section{Justification}

    Since our group was looking for some ludic, non-currency related
    blockchain-based smart contract system, we decided then to create a more
    featureful monster game focusing in being an actual game with richer
    features.

    The use of Blockchain and Smart Contracts, aside being previously required
    for this project, are technologies currently being explored, but most
    usages aims for currency and just a few aims for games, leaving room for
    this work to explore and later report its results.

    In the case of our game, it would allow to estabilish real ownership over
    your monsters, allowing you to buy, sell, and directly trade with other
    players.  Each monster will have it's own randomly generated base
    attributes. By breeding them with other compatible monsters, it is possible
    to pass good attributes over to the next generation, thus increasing the
    potential power of the monster, and it's market value.

    \section{Requirements}

    \subsection{Functional}

    The system must:

    \begin{enumerate}
        \item Allow users to register themselves as players;
        \item Allow players to find, catch and own a \st{Pokémon} monster;
        \item Allow players to trade monsters between themselves if they aggree
              so;
        \item Allow players to train and evolve their monsters;
        \item Allow players to challenge each other with their monsters;
        \item Allow players to bet on which monster will win in a challenge.
        \item Allow players to set their monsters to \st{kill} friendly defeat
              wild monsters for experience points;
        \item Allow players to breed their monsters in order to \textit{mine}
              for new (and hopefully better) monsters;
        \item Allow users to know a monster's stats;
    \end{enumerate}

    \subsection{Non-functional}

    \begin{enumerate}
        \item Monsters will evolve (increase their stats) once they reach a
              certain value of experience points (which will also increase upon
              evolving);
        \item Challenges' results must sound fair (according to later decided
              criteria from this project's authors);
        \item Trading must be done offering monster (and/or money) for monster
              (and/or money).
    \end{enumerate}
\end{document}
